\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-04-29 paper_final.tex
Fixed small issue with proof. y should be -1 instead of 1 for x1

\begin{algorithm}
\caption{Bounding $\eta$ within $\epsilon$ }
\begin{algorithmic}[1]
	\REQUIRE $\epsilon$ , lower bound $\eta_{\min} > 0$, upper bound $\eta_{\max} < \infty$ and $w^*$
	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = 1 = 
	-sign(\langle w_0 , x_1 \rangle )$
	\STATE Give $(x_1, y_1)$ to the perceptron and allow to update.
	\STATE $\alpha \leftarrow \eta_{\min}$
	\STATE $\beta \leftarrow \eta_{\max}$

	\WHILE{$\beta - \alpha > \epsilon$}
		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
		\IF{$\hat{y} = 1$}
			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 		
		\ELSE
			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 
		\ENDIF	
	\ENDWHILE   
	\RETURN $(\alpha , \beta)$
\end{algorithmic}
\end{algorithm}

@@

\textit{Proof.}
Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = 1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
\color{red}
I don't think that its hard to show this is true. But I won't prove for now
\color{black}

@@

Then grab an unlabeled $x_2$ such that
$\langle w_0,x_2 \rangle \neq 0$, $\langle x_1, x_2 \rangle \neq 0$
and 
$$
\langle w_0,x_2 \rangle + \frac{\eta_{\max} - \eta_{\min}}{2} \langle x_1, x_2 \rangle = 0
$$
\color{red}
There should always be at least one solution to this. Again I won't prove for now.
\color{black}

Then probe the learner with $x_2$. If the learner outputs $+1$ then
$\eta \in (\frac{\eta_{\max} - \eta_{\min}}{2} , \eta_{\max}]$, else 
$\eta \in [\eta_{\min},\frac{\eta_{\max} - \eta_{\min}}{2}]$

>>>>

\begin{algorithm}
\caption{Bounding $\eta$ within $\epsilon$ }
\begin{algorithmic}[1]
	\REQUIRE $\epsilon$ , lower bound $\eta_{\min} > 0$, upper bound $\eta_{\max} < \infty$ and $w^*$
	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = -1 = 
	-sign(\langle w_0 , x_1 \rangle )$
	\STATE Give $(x_1, y_1)$ to the perceptron and allow to update.
	\STATE $\alpha \leftarrow \eta_{\min}$
	\STATE $\beta \leftarrow \eta_{\max}$

	\WHILE{$\beta - \alpha > \epsilon$}
		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle - \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
		\IF{$\hat{y} = 1$}
			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 		
		\ELSE
			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 
		\ENDIF	
	\ENDWHILE   
	\RETURN $(\alpha , \beta)$
\end{algorithmic}
\end{algorithm}

@@

\textit{Proof.}
Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = -1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
\color{red}
I don't think that its hard to show this is true. But I won't prove for now
\color{black}

@@

Then grab an unlabeled $x_2$ such that
$\langle w_0,x_2 \rangle \neq 0$, $\langle x_1, x_2 \rangle \neq 0$
and 
$$
\langle w_0,x_2 \rangle - \frac{\eta_{\max} - \eta_{\min}}{2} \langle x_1, x_2 \rangle = 0
$$
\color{red}
There should always be at least one solution to this. Again I won't prove for now.
\color{black}

Then probe the learner with $x_2$. If the learner outputs $-1$ then
$\eta \in (\frac{\eta_{\max} - \eta_{\min}}{2} , \eta_{\max}]$, else 
$\eta \in [\eta_{\min},\frac{\eta_{\max} - \eta_{\min}}{2}]$
